Storing messages with multipartite neural cliques

### 2014-07-18 Articles/article.tex
correction indice

	States of the network are characterized by which units are activated. A message corresponds to one, and only one, state of the network. A message $y$ of length $c$ can be seen as an array $x$ of length $c\dot l$ where for each $j\in [1,c]$, the $j$-th symbol of $y$ denoted $y_j$ is represented by $x[(j-1)l+1\hdots jl]$.\footnote{This is a clustered representation. $x$ is separated in $c$ clusters of $l$ units.} To sum up the $k$-th unit in the $j$-th cluster corresponds to the index $l = (j-1)l+k$. We say the network is in state $x$ if for all $j\in [1, c]$ and $k\in [1,l]$, units $k$ in cluster $j$ of the network is active if, and only if, $x[(j-1)l+l] = 1$.

@@

	Storing a message $y$ in the network amounts to consider the network in state $x\,$%, that is for all $j$ and $k$ such as $1 \le k \le l$ and $1 \le j \le c$, the unit $k$ in the cluster $j$ is activated if and only if $x[(j-1)l+k] = 1$ 
	; then adding all edges between activated units to the network excepting for units sharing the same cluster. Note that edges already present in the network remain unchanged. Thus we obtain a multipartite clique between activated units representing a message.% The parameter $a$ describing the number of activated units per cluster will be called number of activities.

@@

	$\tilde{W} = \max_{x\in \mathcal{M}} x x^{\intercal}$ which is the matrix where all edges between units activated for each state $x$ in the same cluster have been added.
	$W$ can now be expressed as :\vspace*{1mm}

	$W_{ll'} = \bigg \{
  \begin{tabular}{ccc}
  $0$ & if $\exists j\in [1, c], \, (j-1)c+1 \le l,l' \le jc$ \\
  $\tilde{W}_{ll'}$ & otherwise 
  \end{tabular}
  $
  \vspace*{1mm}

>>>>

	States of the network are characterized by which units are activated. A message corresponds to one, and only one, state of the network. A message $y$ of length $c$ can be seen as an array $x$ of length $c\cdot{} l$ where for each $j\in [1,c]$, the $j$-th symbol of $y$ denoted $y_j$ is represented by $x[(j-1)l+1\hdots jl]$.\footnote{This is a clustered representation. $x$ is separated in $c$ clusters of $l$ units.} To sum up the $k$-th unit in the $j$-th cluster corresponds to the index $i = (j-1)l+k$. We say the network is in state $x$ if for all $j\in [1, c]$ and $k\in [1,l]$, units $k$ in cluster $j$ of the network is active if, and only if, $x[(j-1)l+k] = 1$. Taking into account this correspondence between messages $y$ in $\mathcal{M}$ and their clustered representation $x$, we will now also consider $x$ as messages.

@@

	Storing a message $y$ in the network amounts to consider the network in state $x\,$%, that is for all $j$ and $k$ such as $1 \le k \le l$ and $1 \le j \le c$, the unit $k$ in the cluster $j$ is activated if and only if $x[(j-1)l+k] = 1$ 
	; then adding all edges between activated units to the network excepting for units sharing the same cluster. Notice that edges already present in the network remain unchanged throughout the storing process. Thus we obtain a multipartite clique between activated units representing a message.% The parameter $a$ describing the number of activated units per cluster will be called number of activities.

@@

	$\tilde{W} = \max_{x\in \mathcal{M}} x x^{\intercal}$ which is the matrix where all edges between  activated units for each state $x$ in the same cluster have been added.
	$W$ can now be expressed as :\vspace*{1mm}

	$W_{ii'} = \bigg \{
  \begin{tabular}{ccc}
  $0$ & if $\exists j\in [1, c], \, (j-1)l+1 \le i,i' \le jl$ \\
  $\tilde{W}_{ii'}$ & otherwise 
  \end{tabular}
  $
  \vspace*{1mm}
